Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-26 paper/ms.tex
new figure 3
udpates mass ranges

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
We construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
We explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using as observational
constraints the angular correlation function (ACF) and the LAEs number density. 
We find that the preferred minium and maximum masses in our model span
a wide range $10^{9.8}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all models consistent with
observations has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
However, we find that the same individual models have a relatively tight
$1\sigma$ mass gap $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
We are also able show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$. 
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$.
\end{abstract}

@@

We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
algorithm. 
The catalogs were obtained from the publicly available Multidark
database  \footnote{\url{http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. 
For each  halo in the box we extract its comoving position and mass.  
We focus our work on halos more massive than $1.5\times
10^{9}$\hMsun\ resolved with at least  $40$ particles 
to guarantee a well behaved halo mass function. 
We do not take into account sub-halos.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc\. 
  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
  where the number density  of halos is smaller than the number of
  observed LAEs but we consider them as consistent because of the uncertainty
  in the median number density due to cosmic variance. See 
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

The preferred $1-\sigma$ range for the masses is $9.6<\log \mmin<11.0$
and $10.9<\log\mmax<13.0$.
\focc\ is completely determined by \mmin\ from \focc$=$0.015 when
$\log\mmin=9.6$ to $\focc=0.30$ when $\log\mmin=11.0$. 
We compute the power-law dependece between \focc\ and \mmin\ to be 
\begin{equation}
\focc = 0.1\left(\frac{\mmin}{10^{10.5}\hMsun}\right)^{0.93}.
\end{equation}
We remind the reader that models whith $\log \focc>0.00$ ($\focc>1$)
correspond to cases where the halo number density is smaller 
than the number of observed LAEs but are  still considered consistent
because of the expected uncertainty in the median number density of
LAEs due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
\S\ref{subsec:explore}).

>>>>

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
We construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
We explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using as observational
constraints the angular correlation function (ACF) and the LAEs number density. 
We find that the preferred minium and maximum masses in our model span
a wide range $10^{10.0}\hMsun\leq \mmin \leq 10^{11.1}\hMsun$ ,
$10^{11.0}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all models consistent with
observations has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
However, we find that the same individual models have a relatively tight
$1\sigma$ mass gap $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
We are also able show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$. 
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$.
\end{abstract}

@@

We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
algorithm. 
The catalogs were obtained from the publicly available Multidark
database  \footnote{\url{http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. 
For each  halo in the box we extract its comoving position and mass.  
We focus our work on halos more massive than $6.3\times
10^{9}$\hMsun\ resolved with at least  $40$ particles 
to guarantee a well behaved halo mass function. 
We do not take into account sub-halos.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{fig3.pdf}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc\. 
  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
  where the number density  of halos is smaller than the number of
  observed LAEs but we consider them as consistent because of the uncertainty
  in the median number density due to cosmic variance. See 
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

The preferred $1-\sigma$ range for the masses is $10.0<\log \mmin<11.1$
and $11.0<\log\mmax<13.0$.
\focc\ is completely determined by \mmin\ from \focc$=$0.015 when
$\log\mmin=9.8$ to $\focc=0.30$ when $\log\mmin=11.0$. 
We compute the power-law dependece between \focc\ and \mmin\ to be 
\begin{equation}
\focc = 0.1\left(\frac{\mmin}{10^{10.5}\hMsun}\right)^{0.93}.
\end{equation}
We remind the reader that models whith $\log \focc>0.00$ ($\focc>1$)
correspond to cases where the halo number density is smaller 
than the number of observed LAEs but are  still considered consistent
because of the expected uncertainty in the median number density of
LAEs due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
\S\ref{subsec:explore}).
